Efficient N-Dimensional surface estimation using Crofton formula and run-length encoding

### 2011-12-16 article/Article.tex
update section names

@@

\subsection{Implementation}

The number of intercepts, required to use the method described earlier, can be efficiently computed by using the run-length encoding of
the binary objects.

>>>>

\section{Introduction}

@@

\subsection{Intercepts count in digital images}

The intercepts count, required to use the method described earlier, can be efficiently computed by using the run-length
encoding of the binary objects.
